Implementation of a lattice Boltzmann method for immiscible two-phase flow simulations using the level set method

### 2015-11-14 Paper/paper.tex
Reference

With respect to the given definition of the discrete lattice velocities (\ref{disc_vel}), the pressure jump is approximated by,
\begin{equation}
	[p] \approx \frac{1}{3} (\rho(x_2,t)\varrho_2 - \rho(x_1,t)\varrho_1) \text{.}
\end{equation}
and thus, all variables for the boundary conditions are defined.

@@

\bibitem{Thoemmes} {\sc G. TH\"OMMES, J. BECKER}, A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method, J. Comput. Phys. 228 (2009), 1139-1156.

\bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.

>>>>

With respect to the given definition of the discrete lattice velocities (\ref{disc_vel}, see also \cite{Thoemmes2}), the pressure jump is approximated by,
\begin{equation}
	[p] \approx \frac{1}{3} (\rho(x_2,t)\varrho_2 - \rho(x_1,t)\varrho_1) \text{.}
\end{equation}
and thus, all variables for the boundary conditions are defined.

@@

\bibitem{Thoemmes} {\sc G. TH\"OMMES, J. BECKER, M. JuNK, A.K. VAIKUNTAM, D. KEHRWALD, A. KLAR, K. STEINER, A. WIEGMANN}, A lattice Boltzmann method for immiscible multiphase flow simulations using the level set method, J. Comput. Phys. 228 (2009), 1139-1156.

\bibitem{Thoemmes2} {\sc J. BECKER, M. JUNK, D. KEHRWALD, G. TH\"OMMES, Z. YANG}, A combined lattice BGK/level set method for immiscible two-phase flows, Computers and Mathematics with Applications, 58(5):950–964, 2009.
\bibitem{Adalsteinsson} {\sc D. ADALSTEINSSON, J.A. SETHIAN}, The fast construction of extension velocities in level set methods, J. Comput. Phys. 148 (2) (1999) 2–22.
